The \dealii{} Library, Version 9.0

### 2018-04-04 9.0/paper.tex
add

The major changes of this release are:
\begin{itemize}
\item The \texttt{CellDataStorage} ...

>>>>

The major changes of this release are:
\begin{itemize}
\item Manifold smoothing: The manifold smoothing algorithms applied in the Triangulation class and MappingQGeneric have been changed from the old Laplace-style smoothing to a transfinite interpolation that linearly blends between the descriptions on the faces around a cell. The old transformation introduced boundary layers inside cells that prevented convergence rates from exceeding 3.5 in the global L2 errors on typical settings. This change also considerably improves mesh quality on settings where curved descriptions are only applied to the boundary rather than the whole volume.

\item C++11 is now required and used in many places, move semantics, ... (...)

\item
